---
title: "p8105_hw1_csl2209"
author: "Casandra Laney"
date: "2025-09-20"
output: github_document
---


## Problem 1 

Let's import the dataset and load the package

```{r}
library(tidyverse)
library(moderndive)

data("early_january_weather")
```


The dataset 'early_january_weather' contains 15 variables of weather data collected at EWR. 

Important variables include:

* 'temp': the temperature in F.

* 'wind_dir': direction of the wind in degrees

* 'wind_speed': speed of the wind in mph

* 'wind_gust': gust speed of wind in mph

* 'precip': the precipitation in inches

* 'time_hour': the date and hour of the recording

The dataset has `r ncol(early_january_weather)` columns and and `r nrow(early_january_weather)` rows.

The mean temperature is `r mean(early_january_weather$temp)`.

```{r}
ggplot(early_january_weather, 
       aes(x = time_hour, y = temp, color = humid)) + geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 6)
```

**As time increases, the overall temperature increases. Within the overall increase, temperature fluctuates up and down. In the earlier days (~Jan 1-10), there are lower levels of humidity. Humidity reaches an increase around Jan 10-14, hitting max levels of 100.**

## Problem 2

Let's create a dataframe

```{r}
## setting seed for reproducibility
set.seed(20)

example_df = tibble(
  vec_random = rnorm(10),
  vec_logical = vec_random > 0, 
  vec_char = c("My", "name", "is", "Cassie", "and", "coding", "is", "so", "much", "fun"),
  vec_factor = factor(c("high", "medium", "high", "medium", "low", "low", "high", "medium", "low", "high"))
)

## calling on dataframe for easy previewing
example_df
```

Let's try to take the mean of each variable.

* vec_random: `r mean(example_df$vec_random)`

* vec_logical: `r mean(example_df$vec_logical)`

* vec_char: `r mean(example_df$vec_char)`

* vec_factor: `r mean(example_df$vec_factor)`

**The character and factor vectors did not work, while the random and logical vectors did.**

Let's try it again, applying the as.numeric function.

```{r echo=TRUE, results='hide'}
as.numeric(example_df$vec_logical)
as.numeric(example_df$vec_char)
as.numeric(example_df$vec_factor)
```

**'as.numeric' changes the logical vector into 1s and 0s, changes the character vector into NAs, and turns the class values in the factor vector into 1, 2, or 3s. This happens because R cannot assign numbers to arbitrary text. Because the logical and factor vectors have categories that can be assigned integers (class or true/false), it can be turned into a numeric vector.**
