---
title: "p8105_hw1_csl2209"
author: "Casandra Laney"
date: "2025-09-20"
output: github_document
---


## Problem 1 

Let's import the dataset and load the package

```{r}
library(tidyverse)
library(moderndive)

data("early_january_weather")
```


The dataset 'early_january_weather' contains 15 variables of weather data collected at EWR. 

Important variables include:

* 'temp': the temperature in F.

* 'wind_dir': direction of the wind in degrees

* 'wind_speed': speed of the wind in mph

* 'wind_gust': gust speed of wind in mph

* 'precip': the precipitation in inches

* 'time_hour': the date and hour of the recording

The dataset has `r ncol(early_january_weather)` columns and and `r nrow(early_january_weather)` rows.

The mean temperature is `r mean(early_january_weather$temp)`.

```{r}
ggplot(early_january_weather, 
       aes(x = time_hour, y = temp, color = humid)) + geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 6)
```

**As time increases, the overall temperature increases. Within the overall increase, temperature fluctuates up and down. In the earlier days (~Jan 1-10), there are lower levels of humidity. Humidity reaches an increase around Jan 10-14, hitting max levels of 100.**

## Problem 2

Let's create a dataframe

```{r}
## setting seed for reproducibility
set.seed(20)

example_df = tibble(
  vec_random = rnorm(10),
  vec_logical = vec_random > 0, 
  vec_char = c("My", "name", "is", "Cassie", "and", "coding", "is", "so", "much", "fun"),
  vec_factor = factor(c("high", "medium", "high", "medium", "low", "low", "high", "medium", "low", "high"))
)

## calling on dataframe for easy previewing
example_df
```

Let's try to take the mean of each variable.

* vec_random: `r mean(example_df$vec_random)`

* vec_logical: `r mean(example_df$vec_logical)`

* vec_char: `r mean(example_df$vec_character)`

* vec_factor: `r mean(example_df$vec_factor)`

**The character and factor vectors did not work, while the randon=m and logical vectors did.**

Let's try it again, applying the as.numeric function.

```{r}

```

